---
title: "Nobel winners"
author: "John T. Bennett"
date: "dtg"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r load-packages, message=FALSE}
library(tidyverse)
```

Let's first load the data:

```{r label-me1, eval=FALSE}
nobel <- read_csv(file = "data-raw/nobel.csv")
```

*Extract & Count Unique Values in Each Column of Data Frame:
``{r unique}
list_unique <- lapply(nobel, unique)
list_unique
```

"Physics"    "Chemistry"  "Peace"      "Medicine"   "Literature" "Economics"


Then let's split the data into two:
    Create a new data frame, nobel_stem, that filters for the STEM fields (Physics, Medicine, Chemistry, and Economics).
    Create another data frame, nobel_nonstem, that filters for the remaining fields. Tip: Use the %in% operator when filtering

```{r label-me2, eval=FALSE}
# stem laureates
nobel_stem <- nobel %>%
  filter(category %in% c ("Physics", "Medicine", "Chemistry", "Economics"))
```

```{r Non-stem}
# non-stem laureates
nobel_nonstem <- nobel %>%
  filter(category %in% c("Literature", "Peace"))
```

And finally write out the data:
    Write out the two data frames to nobel-stem.csv and nobel-nonstem.csv, respectively, to data/.

nobel <- read_csv(file = "data-raw/nobel.csv")

"write_csv(df, file = "data-raw/df.csv")" gives us 688 obs, 26 vars 

write_csv(df, file = "data-raw/df.csv")

1) nobel-stem.csv 
```{r nobel-stem.csv}
write_csv(nobel_stem, file = "data-raw/nobel_stem.csv")
fs::dir_ls("data-raw")
```

2) nobel-nonstem.csv
```{r nobel-nonstem.csv}
write_csv(nobel_nonstem, file = "data-raw/nobel_nonstem.csv")
```

## References {#references}
1. Assignment Adapted from [Mine Cetinkaya-Rundel's Data Science in a Box](https://github.com/rstudio-education/datascience-box)